Exploratory Analysis

### 2023-11-30 Code/Draft1Rmd.Rmd
Updated line plot

library(tidyverse)
library(ggplot2)
library(Synth)

@@

ggplot()+
  geom_line(data = or_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Oregon")) +
  geom_line(data = ca_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "California")) +
  geom_line(data = wa_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Washington")) +
  scale_color_manual(name = "State",
                     values = c("Oregon" = "blue", "California" = "red", "Washington" = "green")) +
  theme_bw()
```

@@

>>>>

library(tidyverse)
library(ggplot2)
library(Synth)
source("Functions.R")

@@

ggplot()+
  geom_line(data = or_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Oregon")) +
  geom_line(data = ca_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "California")) +
  geom_line(data = wa_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Washington")) +
  scale_color_manual(name = "State",
                     values = c("Oregon" = "blue", "California" = "red", "Washington" = "green")) +
  labs(y = "Log Combined Overdose Deaths")
  theme_bw()
```

@@

```{r results="hide"}
or_yearly2 <- or_yearly
or_yearly2$
```
